Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-14 ms.qmd
Figures sort of sorted for lnRRq10

```{r lnrrq10, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
#############
## lnRRQ10 ##
#############
##################################################
# Organise the data and prune tree
##################################################
# Subset the data
lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% 
                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))

@@

```{r, lncvrq10}
#| echo: false
#| warning: false
#| error: false
#| include: false

@@

### *Does the opportunity for selection differ across terrestrial and aquatic ectotherms?*
```{r, wildlnRR10, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
#######################################
  ## lnRRQ10 from Wild Populations ##
#######################################
##################################################
  # Organise the data and prune tree
##################################################

@@

```{r wildlncvr, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
#######################################
  ## lnCVRQ10 from Wild Populations ##
#######################################
##################################################
  # Organise the data and prune tree
##################################################

>>>>

```{r lnrrq10}
#| echo: false
#| cache: true
#| message: false
#| warning: false
#| include: false

#############
## lnRRQ10 ##
#############
##################################################
# Organise the data and prune tree
##################################################
# Subset the data
lnRRQ10_data <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% 
                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))

@@

```{r, lncvrq10}
#| echo: false
#| warning: false
#| error: false
#| include: false
#| cache: true

@@

### *Does the opportunity for selection differ across terrestrial and aquatic ectotherms?*
```{r, wildlnRR10}
#| cache: true
#| include: false
#| echo: false
#| warning: false
#| 
#######################################
  ## lnRRQ10 from Wild Populations ##
#######################################
##################################################
  # Organise the data and prune tree
##################################################

@@

```{r wildlncvr}
#| cache: true
#| include: false
#| echo: false
#| warning: false
#| 
#######################################
  ## lnCVRQ10 from Wild Populations ##
#######################################
##################################################
  # Organise the data and prune tree
##################################################
